Hydra Battles and Cie

### 2021-03-07 doc/chapter-primrec.tex
renaming of a lemma

\begin{remark}
It is easy to prove that any unary function which dominatates \texttt{fun n => Ack n n} fails to be primitive recursive. We use an instance on \texttt{majorAnyPR} for unary functions.
\vspace{4pt}
\noindent

\emph{From \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR}}.
\begin{Coqsrc}
Lemma majorPR1  (f: naryFunc 1)(Hf : isPR 1 f)
  : exists (n:nat), forall x ,  f x  <= Ack n x.
(* ... *)
\end{Coqsrc}

@@

%%% ICI

% \item Show that for all $n$ and $m$, $A\,n\,m > m$ and  that the functions $A\,n$ are strictly monotonous.

% Show also that, for any $n$ and $m$, $A\,n\,m \leq A\,(n+1)\,m$. 
%          Finally, show that for any $n$, $m$ and $k$, 
% $A\,k\,(A\,m\,n)\leq A\,(2+\textrm{max}(k,m))\,n$.
% \emph{\textbf{Done.}}
% \item Show that for any primitive recursive function $f$ of $k$ arguments,
% for any $x_1,\dots\,x_k$, $f(x_1,\dots,x_k)\leq A\,n\,(x_1+\dots+x_k)$. \emph{\textbf{Still to do.}}
% \item Show that the Ackermann function is not primitive recursive. \emph{\textbf{Still to do.}}

% \end{enumerate}

>>>>

\begin{remark}
It is easy to prove that any unary function which dominatates \texttt{fun n => Ack n n} fails to be primitive recursive. We use an instance of \texttt{majorAnyPR} for unary functions.
\vspace{4pt}
\noindent

\emph{From \href{../theories/html/hydras.MoreAck.AckNotPR.html}{MoreAck.AckNotPR}}.
\begin{Coqsrc}
Lemma majorPR1  (f: naryFunc 1)(Hf : isPR 1 f)
  : exists (n:nat), forall x, f x <= Ack n x.
(* ... *)
\end{Coqsrc}

@@
